Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-07 msbr_reproc.tex
some acronym edits, uses glspl to get plural acronyms.

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor that consists of 
constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
$LiF-BeF_2-ZrF_4-UF_4$) and solid graphite moderator structures. This liquid 
fuel form leads to immediate advantages over traditional, 
solid-fueled, reactors. The molten-salt carrier with dissolved 
fissile and/or fertile material allows for online refuelling and 
reprocessing. Thus, \gls{MSR}s can potentially operate years without shutdown, 
achieving maximum fuel utilization and outstanding neutron economy 
\cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
complex fabrication since the fissile material could be transported from any 
enrichment plant to the \gls{NPP} in the form 
of uranium hexafluoride ($UF_6$).  Additionally, \glspl{MSR} have a high level 
of inherent safety due to their characteristically 
strong negative temperature coefficient of reactivity, near-atmospheric 
pressure in the primary loop, stable coolant, passive decay heat cooling, and 
small excess reactivity \cite{elsheikh_safety_2013}.

The thorium fueled \gls{MSBR} was developed in early 1970s by \gls{ORNL} 
specifically to realize the promise of the thorium fuel cycle which allows the 
use of natural thorium instead of enriched uranium as the fertile element. 
Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment 
\cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
thorium cycle produces much less amount of plutonium and minor actinides (MAs) 
comparing to the traditional uranium fuel cycle, consequently, it might 
significantly increase proliferation resistance when \gls{MSR} operates in the 
breeder regime. The \gls{MSR}s also could be employed as converter reactor for 
transmutation spent fuel from \gls{LWR} or others.

@@

Currently, researchers usually using supporting tools and scripts to simulate 
online reprocessing and refueling. Most researchers investigating the 
\gls{MSR}s have utilised for reprocessing calculations stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) code with originally-developed 
scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}. The 
Serpent 2 is the first code supporting continuous material reprocessing, and 
allows create needed number of material flows into the fuel and/or out from the 
fuel.

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor that consists of 
constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
$LiF-BeF_2-ZrF_4-UF_4$) and solid graphite moderator structures. This liquid 
fuel form leads to immediate advantages over traditional, 
solid-fueled, reactors. The molten-salt carrier with dissolved 
fissile and/or fertile material allows for online refuelling and 
reprocessing. Thus, \glspl{MSR} can potentially operate years without shutdown, 
achieving maximum fuel utilization and outstanding neutron economy 
\cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
complex fabrication since the fissile material could be transported from any 
enrichment plant to the \gls{NPP} in the form 
of uranium hexafluoride ($UF_6$).  Additionally, \glspl{MSR} have a high level 
of inherent safety due to their characteristically 
strong negative temperature coefficient of reactivity, near-atmospheric 
pressure in the primary loop, stable coolant, passive decay heat cooling, and 
small excess reactivity \cite{elsheikh_safety_2013}.

The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} 
specifically to realize the promise of the thorium fuel cycle which allows the 
use of natural thorium instead of enriched uranium as the fertile element. 
Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment 
\cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
thorium cycle produces a reduced quantity of plutonium and \glspl{MA} 
compared to the traditional uranium fuel cycle. Consequently, it may 
significantly increase proliferation resistance when the \gls{MSR} operates in the 
breeder regime. The \glspl{MSR} also could be employed as converter reactor for 
transmutation spent fuel from \gls{LWR} or others.

@@

Currently, researchers usually using supporting tools and scripts to simulate 
online reprocessing and refueling. Most researchers investigating the 
\glspl{MSR} have utilised for reprocessing calculations stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) code with originally-developed 
scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}. The 
Serpent 2 is the first code supporting continuous material reprocessing, and 
allows create needed number of material flows into the fuel and/or out from the 
fuel.
